Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-08-21 main.tex
Update on Overleaf.

@@

    The second inequality follows from Rademacher's theorem when $p = \infty$.
    Let assume that $1 \leq p < \infty$. 
    Suppose that $u \in C^{\infty}(T)$ with support disjoint from $F$.
    Without loss of generality, 
    the segment from to the midpoint of $F$ to the opposing vertex lies on the first coordinate axis,
    and the minimal first coordinate among all the points of $F$ equals $0$. 
    We write $\bfg \in \bfL^{\infty}(T)$ for the trivial extension of $\nabla u$ outside of $T$.
    %With the fundamental theorem of calculus and H\"olders inequality: 
    Now:
    \begin{align*}
        \int_{\Omega} |u(x)|^{p} \diff x \;dx
        &\leq
        \int_{\bbR^{n-1}} \int_{0}^{D} |u( x_{1}, \overline x )|^{p} \;dx_{1} \;d\overline{x}
        \\&
        \leq
        \int_{\bbR^{n-1}} \int_{0}^{D} \left| \int_{0}^{x_{1}} |\bfg( y, \overline x )| \,dy \right|^{p} \;dx_{1} \,d\overline{x}
        \\&
        \leq
        \int_{0}^{D} x_{1}^{p-1} \int_{\bbR^{n-1}} \int_{0}^{x_{1}} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} \,dx_{1}
        \\&
        \leq
        \int_{0}^{D} x_{1}^{p-1} \;dx_1 
        \cdot 
        \int_{\Omega} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} 
        \leq
        \frac{D^{p}}{p} \int_{\Omega} \left| \nabla u( x ) \right|^{p} \,dx
        %
%         \leq
%         \int_{F} |u(x_{1},\dots,x_{n-1},x_{1})|^{p} \,dx_1 \dots \,dx_{n-1} \,dx_{1}
%         \\&
%         \leq
%         \int_{\Omega} \left| \int_{0}^{x_{1}} \partial_{n} u(x_{1},\dots,x_{n-1},y) \,dy \right|^{p} \,dx_1 \dots \,dx_{n-1} \,dx_{1}
%         \\&
%         \leq
%         \int_{\Omega} \int_{0}^{x_{1}} x_{1}^{p-1} \left| \partial_{n} u(x_{1},\dots,x_{n-1},y) \right|^{p} \,dy \,dx_1 \dots \,dx_{n-1} \,dx_{n}
%         \\&
%         \leq
%         \int_{\Omega} \int_{0}^{D} D^{p-1} \left| \bfg(x_{1},\dots,x_{n-1},y) \right|^{p} \,dy \,dx_1 \dots \,dx_{n-1} \,dx_{n}
%         \leq 
%         D^{p} 
%         \int_{\Omega} |\nabla u|^{p} \,dx
        .
    \end{align*}
    That $\|u\|_{L^{p}(\Omega)} \leq \diam(T) \|\nabla u\|_{L^{p}(\Omega)}$ for all $W^{1,p}(T)$ whose members have vanishing trace along $F$ follows from approximation via members of $u \in C^{\infty}(T)$ whose support is disjoint from $F$.

@@

\begin{lemma}
    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
    Smooth forms are dense in $\bfW^{p}\Lambda^{k}(\Omega)$.
    If $\Omega$ is convex, then $C^{\infty}_{c}\Lambda^{k}(\Omega)$ is dense in $\bfW^{p}_{0}\Lambda^{k}(\Omega)$.
\end{lemma}
\begin{proof}
    We notice $\mollifier_{\epsilon} \star u \in C^{\infty}\Lambda^{k}(\bbR^{n})$. 
    By the dominated convergence theorem and because $u$ has a weak derivative,
    for any $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$
    \begin{align*}
        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star u ) \wedge \cartan v 
        &= 
        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge u(y) \wedge \cartan_{x} v(x) \;dx\,dy
        \\&= 
        \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_x\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
        \\&= 
        - \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_y\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
        \\&= 
        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge \cartan_y u(y) \wedge v(x) \;dx\,dy
        = 
        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star \cartan u ) \wedge v 
        .
    \end{align*}
    Hence $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $\bfW^{p}\Lambda^{k}(\Omega)$.

    Next, suppose that $\Omega$ is convex. Without loss of generality, $0 \in \Omega$. 
    Let $u \in \bfW^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
    Define $\varphi_t(x) = tx$ for $t > 1$. 
    Then $\varphi_{t}^{\ast} u \in \bfW^{p}_{0}\Lambda^{k}(t^{-1}\Omega)$ 
    and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
    Given any $t > 1$, by taking the convolution with $\mollifier_{\epsilon}$ for $\epsilon > 0$ small enough,
    we approximate $\varphi_{t}^{\ast} u$ through members of $C^{\infty}_{c}\Lambda^{k}(\Omega)$.
    The desired result follows. 
\end{proof}

@@

\begin{theorem}
    Let $\Omega \subseteq \bbR^{n}$ be convex and let $1 \leq p < \infty$. 
    We have bounded operators 
    \begin{align*}
        \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)
        ,
        \qquad 
        \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)
        .
    \end{align*}
    They satisfy the operator norm bounds 
    \begin{align*}
        \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
        &\leq 
        n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
        D
        \| u \|_{L^{p}(\Omega)}
        ,
        \\
        \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
        &\leq 
        n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
        D
        \| u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    If $u \in \bfW^{p}    \Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in \bfW^{p}    \Alt^{\ell  }(\Omega)$ with $u = \cartan \Poinc_{\ell} u$.
    If $u \in \bfW^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\ell} u \in \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $u = \cartan \Bogov_{\ell} u$.
\end{theorem}
\begin{proof}
    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}\Alt^{\ell}(\Omega)$.

@@

\begin{theorem}\label{theorem:starreflection}
    Let $\calT$ be an $n$-dimensional triangulation and let $S \in \calT$ be a simplex of dimension $k < n$.
    Let $T \in \patch_{\calT}(S)$ be of dimension $n$ and let 
    \begin{align*}
        M := |\patch_{\calT}(S)| \setminus T.
    \end{align*}
    There exists a bi-Lipschitz mapping
    \begin{align*}
        \varphi : T \rightarrow M
    \end{align*}
    satisfying
    \begin{align*}
        \Lip( \varphi,      T ) \leq \Cvier{n}{k} \kappa(\calT)^{2},
        \quad 
        \Lip( \varphi^{-1}, M ) \leq \Cfive{n}{k} \kappa(\calT)^{2},
    \end{align*}
    where $\Cvier{n}{k} \leq ...$ and $\Cfive{n}{k} \leq ...$

@@

        \item 
        % \todo{Combine all this to get the final transformation.}
        We let $\calK$ the simplicial complex obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$. 
        Using our initial observations, we obtain homeomorphisms 
        \begin{align*}
            \Psi_{\calK } : |\calK| \rightarrow \calB,
            \qquad 
            \Psi_{\calR'} : |\calR'| \rightarrow \calB.
        \end{align*}
        Both $\Psi_{\calK}$ and $\Psi_{\calR'}$ map $T$ onto the same subset of the unit ball.
        Consequently, the image under $\Psi_{\calK}$ of $\overline{|\calK| \setminus T}$
        onto the image under $\Psi_{\calR'}$ of $|\calR^{c}|$.
        It follows that 
        \begin{align*}
            \Theta_{S} := \Psi_{\calK}^{-1} \Psi_{\calR'} \Theta
        \end{align*}
        is a mapping from $T$ onto $\overline{\patch_{\calT}(S) \setminus T}$.
        We estimate the Jacobians: 
        \begin{align*}
            \| \Jacobian \Theta_{S} \| 
            \leq 
            \sup_{ K \in \calK  }
            2 \sigma_{\min}(A_{K}^{-1})^{-1} 
            \sup_{ K \in \calR' } 
            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{K}^{-1}) 
            \sup_{ K \in \calR  } \kappa(A_{K})
            .
        \end{align*}
        Each bisection halves the volume of the triangles. Thus,
        \begin{align*}
            \color{red}
            \| \Jacobian \Theta_{S} \| 
            &\leq 
            2 \sup_{ K \in \patch_{\calT}(S) }
            2 \sigma_{\min}(A_{K}^{-1})^{-1} 
            4 \sup_{ K \in \patch_{\calT}(S) } 
            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{K}^{-1}) 
            4 \sup_{ K \in \patch_{\calT}(S) } 
            \kappa(A_{K})
            \\&\leq 
            64
            \left( \sqrt{n} + 1 \right) 
            \sup_{ K \in \patch_{\calT}(S) }
            \sigma_{\max}(A_{K}     ) 
            \sup_{ K \in \patch_{\calT}(S) } 
            \sigma_{\max}(A_{K}^{-1}) 
            \sup_{ K \in \patch_{\calT}(S) } 
            \kappa(A_{K})
            .
        \end{align*}
        That establishes the final estimate.

%         \item 
%         Suppose that $S = \{v_0\}$ is a single vertex. 
%         We construct a transformation from the vertex star around $S$ onto the Euclidean unit ball. 
%         Without loss of generality, $S$ is at the origin. 
%         For any $T \in \patch_{\calT}(S)$, we let $F_T$ be the transformation. 
%         We define $F$ over $|\patch_{\calT}(S)|$ piecewise. 
%         \todo{Complete}
%

@@

\begin{lemma}\label{lemma:PFexteriorsimplex}
    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set. 
    Let $0 \leq k < n$. 
    Then for each $\bfu \in \bfW^{p}\Lambda^{k}(\Omega)$ 
    there exists $\bfw \in \bfW^{p}\Lambda^{k}(\Omega)$ 
    with $\cartan \bfu = \cartan \bfw$ and 
    \begin{align*}
        \| \bfw \|_{L^{p}(\Omega)}
        &
        \leq 
        n A_{\Poinc}(n,k+1) 
        \vol_{n}(B_1(0)) 
        \frac{ \diam(\Omega)^{n} }{|\Omega|} 
        \diam(\Omega)
        \| \cartan \bfu \|_{L^{p}(\Omega)}
        .
    \end{align*}
\end{lemma}
\begin{proof}
    This follows from the discussion in Section~\ref{section:potentialoperator}.
\end{proof}

@@

\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
    Let $T$ be an $n$-simplex 
    and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
    Suppose that $\bfu \in \bfW^{p}\Lambda^{k}(T)$ such that 
    $\trace_{T,F_i} \bfu = 0$ for $0 \leq i \leq l$.
    Then there exists $\bfw \in \bfW^{p}\Lambda^{k}(T)$ such that 
    $\trace_{T,F_i} \bfw = 0$ for $0 \leq i \leq l$
    and  
    \begin{align*}
        \cartan \bfu = \cartan \bfw,
        \quad 
        \| \bfw \| 
        \leq 
        C_{{\rm PF},T,F,k,p}
        \| \cartan \bfu \|
        ,
    \end{align*}
    where $C_{{\rm PF},T,F,k,p} > 0$ is a constant such that 
    \begin{align*}
        C_{{\rm PF},T,F,k,p}
        \leq 
        ...
        \diam(T)
        .
    \end{align*}
\end{lemma}
\begin{proof}
    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F_0$.
    We can also assume that the face of $\hat T$
    orthogonal to the $i$-th coordinate axis is mapped 
    onto the face $F_i$. 
    In what follows, we let $\tilde U$ be the domain obtained from reflecting $\hat T$ along the coordinate axes $l+1$ through $n$.

    We let $\hat u := \varphi^{\ast} u$ and define $\hat g \in \bfL^{p}(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
    Then $\cartan \hat u = \hat g$. 
    We let $\tilde u$ be the extension of $\hat u$ onto $\tilde U$ by reflection across the coordinate axes.
    We define $\tilde g = \cartan \tilde u$
    and see that $\tilde g$ is the extension of $\hat g$ onto $\tilde U$ by reflection across the coordinate axes. 
    By construction, $\tilde u \in \bfW^{p}_{0}\Lambda^{k}(\tilde U)$.

    The bounds for the potential operators imply 
    the existence of $\tilde w \in \bfW^{p}_{0}\Lambda^{k}(\tilde U)$
    with $\cartan \tilde w = \cartan \tilde u$ and 
    \begin{align*}
        \| \tilde w \|_{L^{p}(\tilde U)}
        &\leq 
        n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_2(0)) }{|\Omega|} 
        2
        \| \tilde g \|_{L^{p}(\tilde U)}
        \\&\leq 
        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{|\Omega|} 
        \| \tilde g \|_{L^{p}(\tilde U)}
        .
    \end{align*}
    We let $\bfw \in \bfW^{p}\Lambda^{k}(T)$ be defined by $\bfw := \varphi^{-\ast} \tilde w$.
    By construction, $\cartan \bfw = \cartan \bfu$,
    and $\bfw$ has vanishing trace along the faces $F_{0},\dots,F_{l}$.

    In addition to that, by Theorem~\ref{theorem:pullbackestimate}:
    \begin{gather*}
        \| \bfw \|_{L^{p}(T_{m+1})}
        \leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \| \tilde w \|_{L^{p}(\hat T)}
        \leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \| \tilde w \|_{L^{p}(\tilde U)}
        ,
        \\
        \| \tilde g \|_{L^{p}(\tilde U)}
        \leq 
        2^{\frac n p}
        \| \hat g \|_{L^{p}(\hat T)}
        \leq 
        2^{\frac n p}
        |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi \| \cdot 
        \| \cartan u \|_{L^{p}(T)}
        .
    \end{gather*}
    The second inequality follows.
\end{proof}

>>>>

We also want to compare the diameters of simplices that intersect. We define 
\begin{align}\label{math:diametercomparison}
    \theta(\calT) 
    := 
    \sup_{ \substack{ T, T' \in \subsimplex_{n}(\calT) \\ T \cap T' \neq \emptyset } }
    \frac{ \diam(T) }{ \diam(T') }
\end{align}
We moreover introduce 
\begin{align}\label{math:algebraicshapemeasure}
    \alpha(T)
    := 
    \sup_{ \varphi : \Delta^n \rightarrow T } 
    \frac{ \sigma_{\max}( \Jacobian \varphi ) }{ \sigma_{\max}( \Jacobian \varphi ) }
    ,
    \qquad 
    \alpha(\calT) := \sup_{ T \in \subsimplex_{n}(\calT) } \alpha(T)
    ,
\end{align}
where the first suprenum is taken over all affine transformation from the reference $n$-simplex onto the $n$-simplex $T$.

@@

    The second inequality follows from Rademacher's theorem when $p = \infty$.
    Let assume that $1 \leq p < \infty$. 
    Suppose that $u \in C^{\infty}(T)$ with support disjoint from $F$.
    Without loss of generality, 
    the segment from to the midpoint of $F$ to the opposing vertex lies on the first coordinate axis,
    and the minimal first coordinate among all the points of $F$ equals $0$. 
    We write $\bfg \in \bfL^{\infty}(T)$ for the trivial extension of $\nabla u$ outside of $T$.
    %With the fundamental theorem of calculus and H\"older's inequality: 
    Now:
    \begin{align*}
        \int_{\Omega} |u(x)|^{p} \diff x \;dx
        &\leq
        \int_{\bbR^{n-1}} \int_{0}^{D} |u( x_{1}, \overline x )|^{p} \;dx_{1} \;d\overline{x}
        \\&
        \leq
        \int_{\bbR^{n-1}} \int_{0}^{D} \left| \int_{0}^{x_{1}} |\bfg( y, \overline x )| \,dy \right|^{p} \;dx_{1} \,d\overline{x}
        \\&
        \leq
        \int_{0}^{D} x_{1}^{p-1} \int_{\bbR^{n-1}} \int_{0}^{x_{1}} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} \,dx_{1}
        \\&
        \leq
        \int_{0}^{D} x_{1}^{p-1} \;dx_1 
        \cdot 
        \int_{\Omega} \left| \bfg( y, \overline x ) \right|^{p} \;dy \,d\overline{x} 
        \leq
        \frac{D^{p}}{p} \int_{\Omega} \left| \nabla u( x ) \right|^{p} \,dx
        %
%         \leq
%         \int_{F} |u(x_{1},\dots,x_{n-1},x_{1})|^{p} \,dx_1 \dots \,dx_{n-1} \,dx_{1}
%         \\&
%         \leq
%         \int_{\Omega} \left| \int_{0}^{x_{1}} \partial_{n} u(x_{1},\dots,x_{n-1},y) \,dy \right|^{p} \,dx_1 \dots \,dx_{n-1} \,dx_{1}
%         \\&
%         \leq
%         \int_{\Omega} \int_{0}^{x_{1}} x_{1}^{p-1} \left| \partial_{n} u(x_{1},\dots,x_{n-1},y) \right|^{p} \,dy \,dx_1 \dots \,dx_{n-1} \,dx_{n}
%         \\&
%         \leq
%         \int_{\Omega} \int_{0}^{D} D^{p-1} \left| \bfg(x_{1},\dots,x_{n-1},y) \right|^{p} \,dy \,dx_1 \dots \,dx_{n-1} \,dx_{n}
%         \leq 
%         D^{p} 
%         \int_{\Omega} |\nabla u|^{p} \,dx
        .
    \end{align*}
    That $\|u\|_{L^{p}(\Omega)} \leq \diam(T) \|\nabla u\|_{L^{p}(\Omega)}$ for all $W^{1,p}(T)$ whose members have vanishing trace along $F$ follows from approximation via members of $u \in C^{\infty}(T)$ whose support is disjoint from $F$.

@@

\begin{lemma}
    Let $\Omega \subseteq \bbR^{n}$ be a bounded open set and let $1 \leq p < \infty$. 
    Smooth forms are dense in $W^{p}\Lambda^{k}(\Omega)$.
    If $\Omega$ is convex, then $C^{\infty}_{c}\Lambda^{k}(\Omega)$ is dense in $W^{p}_{0}\Lambda^{k}(\Omega)$.
\end{lemma}
\begin{proof}
    We notice $\mollifier_{\epsilon} \star u \in C^{\infty}\Lambda^{k}(\bbR^{n})$. 
    By the dominated convergence theorem and because $u$ has a weak derivative,
    for any $v \in C^{\infty}_{c}\Lambda^{n-k-1}(\Omega)$
    \begin{align*}
        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star u ) \wedge \cartan v 
        &= 
        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge u(y) \wedge \cartan_{x} v(x) \;dx\,dy
        \\&= 
        \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_x\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
        \\&= 
        - \int_{\bbR^{n}} \int_{\bbR^{n}} \cartan_y\mollifier(x-y) \wedge u(y) \wedge v(x) \;dx\,dy
        \\&= 
        \int_{\bbR^{n}} \int_{\bbR^{n}} \mollifier(x-y) \wedge \cartan_y u(y) \wedge v(x) \;dx\,dy
        = 
        \int_{\bbR^{n}} ( \mollifier_{\epsilon} \star \cartan u ) \wedge v 
        .
    \end{align*}
    Hence $C^{\infty}\Lambda^{k}(\Omega)$ is dense in $W^{p}\Lambda^{k}(\Omega)$.

    Next, suppose that $\Omega$ is convex. Without loss of generality, $0 \in \Omega$. 
    Let $u \in W^{p}_{0}\Lambda^{k}(\Omega)$ and extend $u$ trivially onto $\bbR^{n}$. 
    Define $\varphi_t(x) = tx$ for $t > 1$. 
    Then $\varphi_{t}^{\ast} u \in W^{p}_{0}\Lambda^{k}(t^{-1}\Omega)$ 
    and $\varphi_{t}^{\ast} u$ converges to $u$ as $t$ decreases towards $1$. 
    Given any $t > 1$, by taking the convolution with $\mollifier_{\epsilon}$ for $\epsilon > 0$ small enough,
    we approximate $\varphi_{t}^{\ast} u$ through members of $C^{\infty}_{c}\Lambda^{k}(\Omega)$.
    The desired result follows. 
\end{proof}

@@

\begin{theorem}
    Let $\Omega \subseteq \bbR^{n}$ be convex and let $1 \leq p < \infty$. 
    We have bounded operators 
    \begin{align*}
        \Poinc_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)
        ,
        \qquad 
        \Bogov_{\ell} : L^{p}\Alt^{\ell}(\Omega) \rightarrow \bfW^{p}_{0}\Alt^{\ell-1}(\Omega)
        .
    \end{align*}
    They satisfy the operator norm bounds 
    \begin{align*}
        \| \Poinc_{\ell} u \|_{L^{p}(\Omega)}
        &\leq 
        n A_{\Poinc}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
        D
        \| u \|_{L^{p}(\Omega)}
        ,
        \\
        \| \Bogov_{\ell} u \|_{L^{p}(\Omega)}
        &\leq 
        n A_{\Bogov}(n,\ell) \frac{ \vol_{n}(B_D(0)) }{|\Omega|} 
        D
        \| u \|_{L^{p}(\Omega)}
        .
    \end{align*}
    If $u \in W^{p}    \Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Poinc_{\ell} u \in W^{p}    \Alt^{\ell  }(\Omega)$ with $u = \cartan \Poinc_{\ell} u$.
    If $u \in W^{p}_{0}\Alt^{\ell}(\Omega)$ with $\cartan u = 0$, then $\Bogov_{\ell} u \in W^{p}_{0}\Alt^{\ell-1}(\Omega)$ with $u = \cartan \Bogov_{\ell} u$.
\end{theorem}
\begin{proof}
    The potential operators are linear and the operator norm bounds are satisfied over the dense subspace $C^{\infty}_{c}\Alt^{\ell}(\Omega)$.

@@

\begin{theorem}\label{theorem:starreflection}
    Let $\calT$ be an $n$-dimensional triangulation and let $S \in \calT$ be a simplex of dimension $k < n$.
    Let $T \in \patch_{\calT}(S)$ be of dimension $n$ and let 
    \begin{align*}
        U := |\patch_{\calT}(S)| \setminus T.
    \end{align*}
    There exists a bi-Lipschitz mapping
    \begin{align*}
        \Xi : T \rightarrow U
    \end{align*}
    satisfying
    \begin{align*}
        \Lip( \Xi,      T ) \leq \Cvier{n}{k} \kappa(\calT)^{2},
        \quad 
        \Lip( \Xi^{-1}, U ) \leq \Cfive{n}{k} \kappa(\calT)^{2},
    \end{align*}
    where $\Cvier{n}{k} \leq ...$ and $\Cfive{n}{k} \leq ...$

@@

        \item 
        % \todo{Combine all this to get the final transformation.}
        We let $\calK$ the simplicial complex obtained from $\patch_{\calT}(S)$ via barycentric refinement of $S$. 
        Using our initial observations, we obtain homeomorphisms 
        \begin{align*}
            \Psi_{\calK } : |\calK| \rightarrow \calB,
            \qquad 
            \Psi_{\calR'} : |\calR'| \rightarrow \calB.
        \end{align*}
        Both $\Psi_{\calK}$ and $\Psi_{\calR'}$ map $T$ onto the same subset of the unit ball.
        Consequently, the image under $\Psi_{\calK}$ of $\overline{|\calK| \setminus T}$
        onto the image under $\Psi_{\calR'}$ of $|\calR^{c}|$.
        It follows that 
        \begin{align*}
            \Xi_{S} := \Psi_{\calK}^{-1} \Psi_{\calR'} \Theta
        \end{align*}
        is a mapping from $T$ onto $\overline{\patch_{\calT}(S) \setminus T}$.
        We estimate the Jacobians: 
        \begin{align*}
            \| \Jacobian \Xi_{S} \| 
            \leq 
            \sup_{ K \in \calK  }
            2 \sigma_{\min}(A_{K}^{-1})^{-1} 
            \sup_{ K \in \calR' } 
            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{K}^{-1}) 
            \sup_{ K \in \calR  } \kappa(A_{K})
            .
        \end{align*}
        Each bisection halves the volume of the triangles. Thus,
        \begin{align*}
            \| \Jacobian \Xi_{S} \| 
            &\leq 
            2 
            \sup_{ K \in \patch_{\calT}(S) }
            2 \sigma_{\min}(A_{K}^{-1})^{-1} 
            4 
            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A_{T}^{-1}) 
            4 
            \kappa(A_{T})
            \\&\leq 
            64
            \left( \sqrt{n} + 1 \right) 
            \kappa(A_{T})
            \sigma_{\max}(A_{T}^{-1}) 
            \sup_{ K \in \patch_{\calT}(S) }
            \sigma_{\max}(A_{K}     ) 
            .
        \end{align*}
        We use 
        \begin{gather*}
            \sup_{ K \in \patch_{\calT}(S) }
            \sigma_{\max}(A_{K}) 
            \leq 
            \Ceins{n} 
            \sup_{ K \in \patch_{\calT}(S) }
            \diam(K)
            \leq 
            \Ceins{n} 
            \theta(\calT)
            \sigma_{\max}(A_{T}) 
            .
        \end{gather*}
        % That establishes the final estimate. 
%         \item 
%         Suppose that $S = \{v_0\}$ is a single vertex. 
%         We construct a transformation from the vertex star around $S$ onto the Euclidean unit ball. 
%         Without loss of generality, $S$ is at the origin. 
%         For any $T \in \patch_{\calT}(S)$, we let $F_T$ be the transformation. 
%         We define $F$ over $|\patch_{\calT}(S)|$ piecewise. 
%         \todo{Complete}
%

@@

\begin{lemma}\label{lemma:PFexteriorsimplex}
    Let $\Omega \subseteq \bbR^{n}$ be a convex bounded open set. 
    Let $0 \leq k < n$. 
    Then for each $u \in W^{p}\Lambda^{k}(\Omega)$ 
    there exists $w \in W^{p}\Lambda^{k}(\Omega)$ 
    with $\cartan u = \cartan w$ and 
    \begin{align*}
        \| w \|_{L^{p}(\Omega)}
        &
        \leq 
        n A_{\Poinc}(n,k+1) 
        \vol_{n}(B_1(0)) 
        \frac{ \diam(\Omega)^{n} }{|\Omega|} 
        \diam(\Omega)
        \| \cartan u \|_{L^{p}(\Omega)}
        .
    \end{align*}
\end{lemma}
\begin{proof}
    This follows from the discussion in Section~\ref{section:potentialoperator}.
\end{proof}

@@

\begin{lemma}\label{lemma:mixedbconsimplex:exteriorderivative}
    Let $T$ be an $n$-simplex 
    and let $F_{0},\dots,F_{l}$ be $l+1$ different faces of $T$. 
    Suppose that $u \in W^{p}\Lambda^{k}(T)$ such that 
    $\trace_{T,F_i} u = 0$ for $0 \leq i \leq l$.
    Then there exists $w \in W^{p}\Lambda^{k}(T)$ such that 
    $\trace_{T,F_i} w = 0$ for $0 \leq i \leq l$
    and  
    \begin{align*}
        \cartan u = \cartan w,
        \quad 
        \| w \| 
        \leq 
        C_{{\rm PF},T,F,k,p}
        \| \cartan u \|
        ,
    \end{align*}
    where $C_{{\rm PF},T,F,k,p} > 0$ is a constant such that 
    \begin{align*}
        C_{{\rm PF},T,F,k,p}
        \leq 
        ...
        \diam(T)
        .
    \end{align*}
\end{lemma}
\begin{proof}
    There exists $\varphi : \hat T \rightarrow T_{m+1}$ mapping the convex closure of the $n$ unit vectors onto the face $F_0$.
    We can also assume that the face of $\hat T$
    orthogonal to the $i$-th coordinate axis is mapped 
    onto the face $F_i$. 
    In what follows, we let $\tilde U$ be the domain obtained from reflecting $\hat T$ along the coordinate axes $l+1$ through $n$.

    We let $\hat u := \varphi^{\ast} u$ and define $\hat g \in L^{p}(\hat T)$ via $\hat g := \cartan \varphi^{\ast} u$. 
    Then $\cartan \hat u = \hat g$. 
    We let $\tilde u$ be the extension of $\hat u$ onto $\tilde U$ by reflection across the coordinate axes.
    We define $\tilde g = \cartan \tilde u$
    and see that $\tilde g$ is the extension of $\hat g$ onto $\tilde U$ by reflection across the coordinate axes. 
    By construction, $\tilde u \in W^{p}_{0}\Lambda^{k}(\tilde U)$.

    The bounds for the potential operators imply 
    the existence of $\tilde w \in W^{p}_{0}\Lambda^{k}(\tilde U)$
    with $\cartan \tilde w = \cartan \tilde u$ and 
    \begin{align*}
        \| \tilde w \|_{L^{p}(\tilde U)}
        &\leq 
        n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_2(0)) }{|\Omega|} 
        2
        \| \tilde g \|_{L^{p}(\tilde U)}
        \\&\leq 
        2^{n+1} n A_{\Bogov}(n,k+1) \frac{ \vol_{n}(B_1(0)) }{|\Omega|} 
        \| \tilde g \|_{L^{p}(\tilde U)}
        .
    \end{align*}
    We let $w \in W^{p}\Lambda^{k}(T)$ be defined by $w := \varphi^{-\ast} \tilde w$.
    By construction, $\cartan w = \cartan u$,
    and $w$ has vanishing trace along the faces $F_{0},\dots,F_{l}$.

    In addition to that, by Theorem~\ref{theorem:pullbackestimate}:
    \begin{gather*}
        \| w \|_{L^{p}(T_{m+1})}
        \leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \| \tilde w \|_{L^{p}(\hat T)}
        \leq 
        |\det(\Jacobian \varphi)|^{\frac 1 p} 
        \| \tilde w \|_{L^{p}(\tilde U)}
        ,
        \\
        \| \tilde g \|_{L^{p}(\tilde U)}
        \leq 
        2^{\frac n p}
        \| \hat g \|_{L^{p}(\hat T)}
        \leq 
        2^{\frac n p}
        |\det(\Jacobian \varphi_1)|^{-\frac 1 p} \| \Jacobian \varphi \| \cdot 
        \| \cartan u \|_{L^{p}(T)}
        .
    \end{gather*}
    The second inequality follows.
\end{proof}
